Computer Science House Constitution

### 2022-03-27 constitution.tex
constitution: by-laws don't exist anymore

\asubsubsection{Evaluations Processes}
During the academic year, a House member is evaluated by the Membership Evaluation.
The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
Semi-Annual Evaluations Meetings are open only to current Active Members.
All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
\\* \\*
At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process.
It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
\asubsubsubsection{Membership Evaluation}
The Membership Evaluation process occurs once per academic year.
It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
\asubsubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evaluation passes their Membership Evaluation without being voted on or evaluated by the quorum.
All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
The Membership Evaluation shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Evaluation occurs.
A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

@@

% ARTICLE VII - JUDICIAL
\article{Judicial}
The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution or By-Laws is required, there is a conflict among House Members, or a House interest needs resolution.
\asection{Formation of a Judicial Board}
A Judicial Board is made up of the Chairperson, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
If either the Chairperson or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
\asection{Judicial Investigation}
The Judicial Board will be responsible for making all necessary inquiries into the matter of the request brought to the Judicial Board.
\asection{Judicial Ruling}
The Judicial Board may present an official ruling following the Judicial Investigation.
This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
\end{document}

>>>>

\asubsubsection{Evaluations Processes}
During the academic year, a House member is evaluated by the Membership Evaluation.
The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
Semi-Annual Evaluations Meetings are open only to current Active Members.
All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
\\* \\*
At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution used during the respective Evaluation Process.
It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
\asubsubsubsection{Membership Evaluation}
The Membership Evaluation process occurs once per academic year.
It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
\asubsubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evaluation passes their Membership Evaluation without being voted on or evaluated by the quorum.
All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
The Membership Evaluation shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Evaluation occurs.
A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

@@

% ARTICLE VII - JUDICIAL
\article{Judicial}
The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among House Members, or a House interest needs resolution.
\asection{Formation of a Judicial Board}
A Judicial Board is made up of the Chairperson, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
If either the Chairperson or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
\asection{Judicial Investigation}
The Judicial Board will be responsible for making all necessary inquiries into the matter of the request brought to the Judicial Board.
\asection{Judicial Ruling}
The Judicial Board may present an official ruling following the Judicial Investigation.
This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
\end{document}
